The development of infants' responses to mispronunciations: A Meta-Analysis

### 2019-11-24 VonHolzenBergmann_MPMetaAnalysis.Rmd
Monster Paper update
incorporated Christina's comments from the summer, finished Discussion, updated references

author: 
  - name          : "Katie Von Holzen"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "0221A LeFrak Hall, University of Maryland, College Park, MD 20742"
    email         : "katie.m.vonholzen@gmail.com"
  - name          : "Christina Bergmann"
    affiliation   : "3,4"

affiliation:
  - id            : "1"
    institution   : "Department of Hearing and Speech Sciences, University of Maryland, USA"
  - id            : "2"
    institution   : "Laboratoire Psychologie de la Perception, Université Paris Descartes"
  - id            : "3"
    institution   : "Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands"
  - id            : "4"
    institution   : "LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University"

@@

abstract: |
  As they develop into mature speakers of their native language, infants must not only learn words but also the sounds that make up those words. To do so, they must strike a balance between accepting some variation (e.g. mood, voice, accent), but appropriately rejecting variation when it changes a word's meaning (e.g. cat vs. hat). We focus on studies investigating infants' ability to detect mispronunciations in familiar words, which we refer to as mispronunciation sensitivity. The goal of this meta-analysis was to evaluate the development of mispronunciation sensitivity in infancy, allowing for a test of competing mainstream theoretical frameworks. The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects. Interestingly, this ability is not modulated by age or vocabulary size, challenging existing theories and suggesting that a mature understanding of native language phonology is present in infants from an early age, possibly before the vocabulary explosion. Despite this finding, we discuss potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations to improve best practices in the study of mispronunciation sensitivity.

@@

  At the turn of the millenium, infant language acquisition researchers had established that during their first two years of life, infants are sensitive to changes in the phonetic detail of newly segmented words [@Jusczyk1995] and learned minimal pairs [@Stager1997]. Furthermore, when presented with familiar image pairs, children fixate on the referent of a spoken label [@Fernald1998; @Tincoff1999]. @Swingley2000 were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g. a baby and a dog) and their eye movements to each image were recorded. On "correct" trials, children heard the correct label for one of the images (e.g. "baby"). On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g. "vaby"). The mean proportion of fixations to the target image (here: a baby) was calculated separately for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL). Mean fixations in correct trials were significantly greater than in mispronounced trials, and in both conditions looks to the target were significantly greater than chance. We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance in each condition as *object identification*. @Swingley2000 concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.

  In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g. cat-hat). The study of @Swingley2000 as well as subsequent studies examining mispronunciation sensitivity probe this latter distinction. Phonological contrasts relevant for the infant language-learner are determined by their native language. For an infant learning Catalan, the vowel contrast /e/-/E/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish. These contrasts are therefore not inate, but must be learned. In this meta-analysis, we focus on infants' developing ability to correctly apply the phonological distinctions for their native language during word recognition. By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; for a notable exception). Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

  Research following the seminal study by @Swingley2000 has extended mispronunciation sensitivity to infants as young as 8 to 10 months [@Bergelson2017], indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations. Regarding the change in mispronunciation sensitivity over development, however, only about half of studies have compared more than one age group on the same mispronunciation task (see Table 1). Across single studies all possible patterns of development lined out above have been reported, making the current meta-analysis very informative.

Several studies have found evidence for *greater* mispronunciation sensitivity as children develop. More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop. @Mani2007 tested 15-, 18-, and 24-month-olds learning British English; although all three groups were sensitive to mispronunciations, 15-month-olds showed a less robust sensitivity. An increase in sensitivity to mispronunciations has also been found from 20 to 24 months [@vanderFeest2015] and 15 to 18 months [@Altvater2014] in Dutch infants, as well as German infants from 22 to 25 months [@Altvater2010]. Furthermore, @vanderFeest2015 found that sensitivity to specific kinds of mispronunciations develop at different ages depending on language infants are learning. In other words, the native language constraints which *kinds* of mispronunciations infants are sensitive to first, and that as infants develop, they become sensitive to other mispronunciations.

@@

  Why would mispronunciation sensitivity change as infants develop? Typically, a change in mispronunciation sensitivity is thought to occur along with an increase in vocabulary size, particularly with the vocabulary spurt at about 18 months. As infants learn more words, their focus shifts to the relevant phonetic dimensions needed for word recognition. For example, an infant who knows a handful of words with few phonological neighbors would not need to have fully specified phonological representations in order to differentiate between these words. As more phonologically similar words are learned, however, the need for fully detailed phonological representations increases [@CharlesLuce1995]. Furthermore, a growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the detail of their phonological representation [@Barton1980]. If vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship between vocabulary size and mispronunciation sensitivity.

  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship [@Swingley2000; @Swingley2002; @Swingley2009; @Zesiger2012; @Mani2008; @Bailey2002; @Mani2007; @Ballem2005]. One notable exception comes from @Mani2010kepstups. Here, 12-month-old infants were divided into a low and high vocabulary group based on median vocabulary size. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations. Taken together, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity. In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to better understand the variation in experimental results.

  Although all mispronunciation sensitivity studies are generally interested in the the phonological detail with which infants represent familiar words, many studies pose more nuanced questions. These questions concern issues at the intersection of phonological development and lexical processing and often result in manipulations of the stimuli and experimental procedure. These manipulations may impact our overall estimate of the effect size of mispronunciation sensitivity. Next to the core investigation of the shape of development of infants' mispronunciation sensitivity, we take the opportunity of a systematic aggregation of data to address these questions and the influence of these manipulations on infants' ability to detect mispronunciations and how this may change with development.

  In designing their mispronunciation stimuli, Swingley and Aslin (2000) chose consonant mispronunciations that were likely to confuse adults (Miller & Nicely, 1955). Subsequent research has settled on systematically modulating phonemic features to achieve mispronunciations of familiar words. By utilizing mispronunciations consisting of phonemic changes, these experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level (i.e. 1-feature, 2-features, 3-features, etc.). The importance of controlling for the degree of phonological mismatch, as measured by number of features changed, is further highlighted by studies that find graded sensitivity to both consonant (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes. The greater the number of features changed, or *mispronunciation size*, the easier it may be to detect a mispronunciation, whereas more similar mispronunciations may be more difficult to detect.

  Although most research examining sensitivity to mispronunciations follows a similar design, there are some notable differences. For example, Swingley and Aslin (2000) presented infants with pairs of familiar images, one serving as the labeled target and one as the unlabeled distractor. In contrast, White and Morgan (2008; see also Mani & Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects. By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, & Hansen, 2003). Infants ages 24 and 30 months associate a novel label with an unfamiliar object, although only 30-month-olds retained this label-object pairing (Bion, Borovsky, and Fernald, 2013). In contrast, 18-month-olds did not learn to associate a novel label with an unfamiliar object, providing evidence that this ability is developing from 18 to 30 months. We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar. Although mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared, the baseline preference for familiar compared to novel stimuli is also thought to change as infants develop (Hunter & Ames, 1988).  Furthermore, young children have been found to look longer at objects for which they know the name, compared to objects of an unknown name (Schafer & Plukett, 1998). In other words, in absentia of a label, infants may be more or less likely to fixate on an unfamiliar object. To account for inherent preferences to the target or distractor image, mispronunciation experiments typically compare the increase in fixations to the target image from a silent baseline to post-labeling or present the same yoked pairs of target and distractor images in in both a correct and mispronounced labelling context. Considering this evidence, we may expect that in older, but not younger, children, the presence of an unfamiliar distractor may lead to greater mispronunciation sensitivity than in the presence of a familiar distractor.

  Furthermore, when presenting infants with a familiar distractor image, some studies control the *phonological overlap between target and distractor labels*. For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck". This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingley, & Pinto, 2001). Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change. The influence of distractor overlap also depends on the *position of mispronunciation* in the word, which can be at word onset, medial, or final positions. Models of spoken word processing place more or less importance on the position of a phoneme in a word. The COHORT model (Marslen-Wilson & Zwitserlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.  In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.

  TRACE has also been used to model infants' sensitivity to mispronunciation position (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth. In early language acquisition, infants typically know more consonant compared to vowel onset words. When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations. The prevalence of consonant onset words may contribute to the finding that consonants carry more weight in lexical processing (C-bias; see Nazzi, Poltrock, & Von Holzen, 2016 for a recent review). In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels. English-learning 12-, 15-, 18-, and 24-month-olds (Mani & Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds (Hojen et al., unpublished) demonstrate similar sensitivity to consonant and vowel mispronunciations. One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations (Swingley, 2016). The English-learning infants tested by Swingley were older than previous studies (mean age 28 months). In word learning, the C-bias has been found to develop later in English learning infants (Floccia, Nazzi, Delle Luche, Poltrock, & Goslin, 2014; Nazzi, Floccia, Moquet, & Butler, 2009). In the current meta-analysis, we attempt to synthesize studies examining sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016). We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages (Nazzi et al., 2016).

  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Table 1). Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare. Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.

In sum, the studies we have reviewed begin to paint a picture of the development of infants' mispronunciation sensitivity. Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of the big picture of early language development. Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and of their mispronunciations sensitivity. Because we aggregate data over various age groups, this meta-analysis can also investigate the role of maturation by assessing the impact of age and vocabulary size. We also make hands-on recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses [@Bergmann2018].

@@

1 Condition: Were words mispronounced or not;  
2 Mean age reported per group of infants, in days;  
3 Vocabulary size, measured by a standardized questionnaire or list;    
4 Size of mispronunciation, measured in features changed;  
5 Distractor familiarity: familiar or unfamiliar;  
6 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;  
7 Position of mispronunciation: onset, medial, offset, or mixed;  
8 Type of mispronunciation: consonant, vowel, or both.

@@

[^1]: Two papers tested bilingual infants (Ramon-Casas & Bosch, 2010; Ramon-Casas et al., 2011), yielding `r bil_infants` experimental conditions. Due to this small number, we do not investigate the role of multilingualism, but do note that removing these papers from the meta-analysis did not alter the pattern of results.

@@

The models reported here are multilevel random-effects models of variance-weighted effect sizes, which we computed with the R [@R] package metafor [@metafor]. To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we first introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model. Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the R [@R] package meta [@meta]. Finally, for a subsequent exploratory investigation of experimental characteristics, we introduced each characteristic as a moderator (more detail below).

@@

Figure \@ref(fig:Vocab-describe1) plots the year of publication for all the mispronunciation sensitivity studies included in this meta-analysis. This figure illustrates two things: the increasing number of mispronunciation sensitivity studies and the decreasing number of mispronunciation studies measuring vocabulary. The lack of evidence for a relationship between mispronunciation sensitivity and vocabulary size in some early studies may have contributed to increasingly fewer researchers including vocabulary measurements in their mispronunciation sensitivity experimental design. This may explain our underpowered analysis of the relationship between object recognition for correct pronunciations and mispronunciations and vocabulary size.

@@

```{r Vocab-describe1, echo = FALSE, fig.width=10,fig.height=8, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (orange), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (green).", results="hide"}
#how did vocabulary collection change over time?

@@

The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age and increased vocabulary size. The results seem clear: Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a constant and stable effect of mispronunciation sensitivity. This did not change with development, and we might consider age a proxy for vocabulary size. We observe that the data for directly reported vocabulary size were too sparse to draw strong conclusions. In the literature, evidence for all possible developmental trajectories has been found, including mispronunciation sensitivity that increases, decreases, or does not change with age or vocabulary size. The present results do lend some support for the proposal that mispronunciation sensitivity stays consistent as infants develop. Furthermore, although we found a relationship between vocabulary size (comprehension) and target looking for correct pronunciations, we found no relationship between vocabulary and target looking for mispronunciations. This may be due to too few studies including reports of vocabulary size and more investigation is needed to draw a firm conclusion.

Alternatively, the lack of developmental change in mispronunciation sensitivity could be due to differences in the types of tasks given to infants of different ages. If infants' word recognition skills are generally thought to improve with age and vocabulary size, research questions that tap more complex processes may be more likely to be investigated in older infants. In the following section, we investigate the role that different moderators play in mispronunciation sensitivity. To investigate the possibility of systematic differences in the tasks across ages, we additionally include an exploratory analysis of whether different moderators and experimental design features were included at different ages.

@@

To understand the relationship between mispronunciation size and mispronunciation sensitivity, we  evaluated the effect size Hedges' *g* with number of features changed as a moderator. The moderator test was significant, `r mod_test(rma_NFeatures)`. Hedges' *g* for number of features changed was `r g_SE(sum_eff)`, which indicated that as the number of features changed increased, the effect size Hedges' *g* significantly decreased `r CI_p(sum_eff)`. We plot this relationship in Figure \@ref(fig:PlotFeatEffect). This confirms previous findings of a graded sensitivity to the number of features changed for both consonant (Bernier & White, 2017; Tamasi, 2016; White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) mispronunciations as well as the importance of controlling for the degree of phonological mismatch in experimental design.

>>>>

author: 
  - name          : "Katie Von Holzen"
    affiliation   : "1,2,3"
    corresponding : yes    # Define only one corresponding author
    address       : "Emil-Figge-Straße 50, 44221 Dortmund, Germany"
    email         : "katie.m.vonholzen@gmail.com"
  - name          : "Christina Bergmann"
    affiliation   : "4,5"

affiliation:
  - id            : "1"
    institution   : "Lehrstuhl Linguistik des Deutschen, Schwerpunkt Deutsch als Fremdsprache/Deutsch als Zweitsprache, Technische Universität Dortmund"
  - id            : "2"
    institution   : "Department of Hearing and Speech Sciences, University of Maryland, USA"
  - id            : "3"
    institution   : "Laboratoire Psychologie de la Perception, Université Paris Descartes"
  - id            : "4"
    institution   : "Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands"
  - id            : "5"
    institution   : "LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University"

@@

abstract: |
  As they develop into mature speakers of their native language, infants must not only learn words but also the sounds that make up those words. To do so, they must strike a balance between accepting the speaker's variation (e.g. mood, voice, accent), but appropriately rejecting variation when it changes a word's meaning (e.g. cat vs. hat). We focus on studies investigating infants' ability to detect mispronunciations in familiar words, which we refer to as mispronunciation sensitivity. The goal of this meta-analysis was to evaluate the development of mispronunciation sensitivity in infancy, allowing for a test of competing mainstream theoretical frameworks. The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects. Interestingly, this ability is not modulated by age or vocabulary size, challenging existing theories and suggesting that a mature understanding of native language phonology is present in infants from an early age, possibly before the vocabulary explosion.Further examining our findings, we shed light on the impact of data analysis choices that may lead to different conclusions regarding the development of infants' mispronunciation sensitivity. Our paper concludes with recommendations for improved practice in testing infants' word and sentence processing on-line.

@@

  At the turn of the millenium, infant language acquisition researchers had established that during their first two years of life, infants are sensitive to changes in the phonetic detail of newly segmented words [@Jusczyk1995] and learned minimal pairs [@Stager1997]. Furthermore, when presented with familiar image pairs, children fixate on the referent of a spoken label [@Fernald1998; @Tincoff1999]. @Swingley2000 were the first to tie these lines of research together and investigate how infants interpret phonological variation in familiar word recognition: Children aged 18 to 23 months learning American English saw pairs of images (e.g. a baby and a dog) and their eye movements to each image were recorded. On "correct" trials, children heard the correct label for one of the images (e.g. "baby"). On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g. "vaby"). Although infants looked at the correct, target image in response to both types of trials, correct trials elicited a greater proportion of looks to the correct, target image than mispronounced trials. @Swingley2000 concluded that already before the second birthday, children's representations for familiar words are phonologically well specified.

  In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g. cat-hat). The study of @Swingley2000 as well as subsequent studies examining infants' application of phonological categories during word recognition through the mispronunciation sensitivity paradigm probe this latter distinction. Phonological contrasts relevant for the infant language-learner are determined by their native language. For an infant learning Catalan, the vowel contrast /e/-/E/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish. These contrasts are therefore not innate, but must be learned. In this meta-analysis, we focus on infants' developing ability to correctly apply the phonological distinctions for their native language during word recognition. By aggregating all publicly available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; @MB1; for a notable exception). Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

  Research following the seminal study by @Swingley2000 has extended mispronunciation sensitivity to infants as young as 8 to 10 months [@Bergelson2017], indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations. Regarding the change in mispronunciation sensitivity over development, however, only about half of studies have compared more than one age group on the same mispronunciation task (see Table 1). Those studies find all possible patterns of development (see below), rendering conclusions regarding developmental change in mispronunciation sensitivity difficult.

Several studies have found evidence for *greater* mispronunciation sensitivity as children develop. More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop. @Mani2007 tested 15-, 18-, and 24-month-olds learning British English; although all three groups were sensitive to mispronunciations, 15-month-olds showed a less robust sensitivity. An increase in sensitivity to mispronunciations has also been found from 20 to 24 months [@vanderFeest2015] and 15 to 18 months [@Altvater2014] in Dutch infants, as well as German infants from 22 to 25 months [@Altvater2010].

@@

  Given the diverse evidence for developmental change, or lack thereof, the question arises as to what could be driving these differences. As infants develop, the rate at which they learn words increases and their focus shifts to the relevant phonetic dimensions needed for word recognition. For example, an infant who knows a handful of words with few phonological neighbors would not need to have fully specified phonological representations in order to differentiate between these words. As more phonologically similar words are learned, however, the need for fully detailed phonological representations increases [@CharlesLuce1995]. Furthermore, a growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the detail of their phonological representation [@Barton1980]. If vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship between vocabulary size and mispronunciation sensitivity.

  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have concluded that there is no relationship [@Swingley2000; @Swingley2002; @Swingley2009; @Zesiger2012; @Mani2008; @Bailey2002; @Mani2007; @Ballem2005]. One notable exception comes from @Mani2010kepstups. Here, 12-month-old infants were divided into low and high vocabulary groups. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations. Taken together, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity. In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to better understand the variation in experimental results.

  An alternative explanation is the level of task difficulty infants are presented with in mispronunciation sensitivity experiments. Although all mispronunciation sensitivity studies are generally interested in the the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed or the position of the mispronunciation. Some studies may differ in their experimental design, presenting a distractor image that overlaps with the target image in the onset phoneme or a completely novel, unfamiliar distractor image. These experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete. The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2011; @Curtin2007; @Werker2005) describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail. The ability to access and use this detail, however, is governed by the task or developmental demands (discrimination vs. word learning) probed in a particular experiment. In a particularly demanding task, such as when the target and distractor image share the same onset phoneme, infants' ability to access the phonological detail of familiar words may be restricted.

  These manipulations may impact task demands, but they are also theoretically interesting, focus on issues at the intersection of phonological development and lexical processing. For specific questions where we can aggregate multiple studies, we take the opportunity to shine a meta-analytic light on what modulates infants' ability to detect mispronunciations in follow-up exploatory analyses. We outline below first which nuanced questions have been frequently asked to provide a more in-depth overview of the current literature.

  The first set of questions concern how infants' sensitivity is modulated by different kinds of mispronunciations. Some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level (i.e. 1-feature, 2-features, 3-features, etc.), finding graded sensitivity to both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] feature changes. This also has consequences for task demands, as the greater the number of features changed, or *mispronunciation size*, the easier it may be to detect a mispronunciation, whereas more similar mispronunciations may be more difficult to detect.

  Models of spoken word processing place more or less importance on the position of a phoneme in a word. The COHORT model [@Marslen-Wilson1989] describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word. In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations. The *position of mispronunciation* in the word may therefore differentially interrupt the infant's word recognition process, with onset mispronunciations resulting in a more demanding task than medial or coda mispronunciations.

  In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*. For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck". This ensures that infants can not use the onset of the word to differentiate between the target and distractor images [@Fernald2001a]. Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.

  Consonantal changes may be more disruptive to lexical processing than vowel changes [@Nazzi2018], which has been extended to infancy [@Nazzi2016]. In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels. English-learning 12-, 15-, 18-, and 24-month-olds [@Mani2007; @Mani2010kepstups] and Danish-learning 20-month-olds [@Hojen] demonstrate similar sensitivity to consonant and vowel mispronunciations. One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations [@Swingley2016]. The English-learning infants tested by Swingley were older than previous studies (mean age 28 months). In word learning, the C-bias has been found to develop later in English- than French-learning infants [@Floccia2014; @Nazzi2009a]. In the current meta-analysis, we attempt to synthesize studies examining sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages to determine whether infants generally exhibit more sensitivity to consonant compared to vowel mispronunciations in familiar word recognition as predicted by a learned account of C-bias emergence [@Floccia2014; @Nazzi2016; @Keidel2007]. We further examine the impact of language family on mispronunciation sensitivity to consonants and vowels, as C-bias emergence has been found to have a different developmental trajectory for Romance (French, Italian) compared to Germanic (British English, Danish) languages [@Nazzi2016].

  A second question is whether the non-linguistic context modulates infants' responses to mispronunciations: Most research on the topic presents infants with two known words, thus ruling out the unlabeled competitor, or distractor, as possible target. In contrast, other studies present infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016]. By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied [@Halberda2003; @Markman2003]. In a learning context, 24- and 30-month-olds associate a novel label with an unfamiliar object, but 18-month-olds do not, providing evidence that this ability, known as mutual exclusivity, is developing from 18 to 30 months [@Bion2013]. We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar. This is a particularly fruitful question to investigate within the context of a meta-analysis, as mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared.

  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (see Table 1). Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare. Indeed, the majority of studies focus on infants learning English as a native language and a sufficient sample of other languages is therefore lacking. Although we do not explicitly compare overall mispronunciation sensitivity by language (although see previous paragraph for rationale to test by language family), we assess evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach.

In sum, the studies we have reviewed begin to paint a picture of the development of infants' use of phonological detail in familiar word recognition. Each study contributes one separate brushstroke and it is only by examining all of them together that we can achieve a better understanding of the big picture of early phono-lexical development. Meta-analyses can provide unique insights by estimating the population effect, both of infants' responses to correct and mispronounced labels, and of their mispronunciations sensitivity. Because we aggregate data over various age groups, this meta-analysis can also investigate the role of maturation by assessing the impact of age and vocabulary size. We also explore the influence of different linguistic (mispronunciation size and position, target-distractor overlap, and type of mispronunciation) and non-linguistic (distractor familiarity) demands on the study of mispronunciation sensitivity. Finally, we explore potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations for experiment planning, for example by providing an effect size estimate for a priori power analyses [@Bergmann2018].

@@

1 Condition: Were words mispronounced or not;  
2 Mean age reported per group of infants, in days;  
3 Vocabulary size, measured by a standardized questionnaire or list;    
4 Size of mispronunciation, measured in features changed;  
5 Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;  
6 Position of mispronunciation: onset, medial, offset, or mixed;  
7 Type of mispronunciation: consonant, vowel, or both.
8 Distractor familiarity: familiar or unfamiliar;

@@

[^1]: Two papers tested bilingual infants [@Ramon-Casas2009; @Ramon-Casas2010], yielding `r bil_infants` experimental conditions. Due to this small number, we do not investigate the role of multilingualism, but do note that removing these papers from the meta-analysis did not alter the pattern of results.

@@

The models reported here are multilevel random-effects models of variance-weighted effect sizes, which we computed with the R [@R] package metafor [@metafor]. To investigate how development impacts mispronunciation sensitivity, our core theoretical question, we first introduced age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44) as a moderator to our main model. Second, we analyzed the correlation between reported vocabulary size and mispronunciation sensitivity using the R [@R] package meta [@meta]. For a subsequent exploratory investigation of experimental characteristics, we introduced each as a moderator: size of mispronunciation, position of mispronunciation, phonological overlap between target and distractor labels, type of mispronunciation, and distractor familiarity (more detail below).

@@

Figure \@ref(fig:Vocabdescribe1) plots the year of publication for all the mispronunciation sensitivity studies included in this meta-analysis. This figure illustrates two things: the increasing number of mispronunciation sensitivity studies and the decreasing number of mispronunciation studies measuring vocabulary. The lack of evidence for a relationship between mispronunciation sensitivity and vocabulary size in some early studies may have contributed to increasingly fewer researchers including vocabulary measurements in their mispronunciation sensitivity experimental design. This may explain our underpowered analysis of the relationship between object recognition for correct pronunciations and mispronunciations and vocabulary size.

@@

```{r Vocabdescribe1, echo = FALSE, fig.width=10,fig.height=8, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (orange), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (green).", results="hide"}
#how did vocabulary collection change over time?

@@

The main goal of this paper was to assess mispronunciation sensitivity and its maturation with age and increased vocabulary size. The results seem clear: Although infants consider a mispronunciation to be a better match to the target image than to a distractor image, there was a constant and stable effect of mispronunciation sensitivity across all ages. In the literature, evidence for all possible developmental trajectories has been found, including mispronunciation sensitivity that increases, decreases, or does not change with age or vocabulary size. The present results do lend some support for the proposal that mispronunciation sensitivity stays constant as infants develop. Furthermore, although we found a relationship between vocabulary size (comprehension) and target looking for correct pronunciations, we found no relationship between vocabulary and target looking for mispronunciations. This may be due to too few studies including reports of vocabulary size and more investigation is needed to draw a firm conclusion.

The studies examined in this meta-analysis examined mispronunciation sensitivity, but many also included more specific questions aimed at uncovering more detailed phonological processes at play during word recognition. Not only are these questions theoretically interesting, they also have the potential to change the difficulty of a msipronunciation sensitivity experiment. It is possible that the lack of developmental change in mispronunciation sensitivity found by our meta-analysis does not capture a true lack of change, but is instead influenced by differences in the types of tasks given to infants of different ages. If infants' word recognition skills are generally thought to improve with age and vocabulary size, research questions that tap more complex processes may be more likely to be investigated in older infants. In the following section, we investigate the role that different moderators play in mispronunciation sensitivity. To investigate the possibility of systematic differences in the tasks across ages, we additionally include an exploratory analysis of whether different moderators and experimental design features were included at different ages.

@@

```{r PlotFeatEffect, echo = FALSE, fig.width=10,fig.height=6, fig.cap="Effect sizes for correct pronunciations, 1-, 2-, and 3-feature mispronunciations.", results="hide"}
